Cognate Priming

### 2023-09-18 docs/index.qmd

# load target objects
tar_load(c(participants, stimuli, 
		   attrition_trials,
		   attrition_participants,
		   gaze_aoi, vocabulary,
		   loos_aggregated, loos_timecourse,
		   data_time, data_summary))

>>>>

# load target objects
tar_load(c(participants, stimuli, 
		   attrition_trials,
		   attrition_participants,
		   gaze_aoi, vocabulary,
		   loos_aggregated, loos_timecourse,
		   data_time, data_summary,
		   model_fits_related,
		   model_fits_cognate))
